The Spine of American Legal Practice

### 2016-06-24 article/article.Rmd
Give part 2 a title

---
title: The Spine of American Legal Practice
author:
- Kellen Funk
- Lincoln Mullen
output: 
  pdf_document:
    number_sections: true
    fig_caption: true
fontsize: 12pt
documentclass: article
...

@@

# The origin and migration of the Field Code

@@

# Part 2

>>>>

---
title: The Spine of American Legal Practice
author:
- Kellen Funk
- Lincoln Mullen
output: 
  pdf_document:
    number_sections: false
    fig_caption: true
fontsize: 12pt
documentclass: article
...

@@

# 1. The origin and migration of the Field Code

@@

# 2. Detecting borrowings among procedure codes
